`flippant` -- An `R` package for the automated analysis of dithionite scramblase

### 2015-09-25 inst/manuscript/manuscript.rmd
Add an draft abstract;
Fix "Mike" to "Michael", as advised by Birgit Ploier;
Typo;

---
title: '`flippant` -- An `R` package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^, Mike A.
  Goren ^‡^ and Anant K. Menon ^‡^
date: "September 19, 2015"
output:
#  word_document
  pdf_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

@@

Mean values of fit constant $\alpha$) correspond with 
`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
respectively, very well to the prior manual analysis by 
@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
of the data we conclude in @ploier_perturbed_submitted that the mutant 
rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data, shows identical trends and close matches of the
results, supporting identical conclusions.

>>>>

---
title: '`flippant` -- An `R` package for the automated analysis of dithionite scramblase
  assays'
author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
date: "September 24, 2015"
output:
#  word_document
  pdf_document:
    fig_caption: yes
csl: bioinformatics.csl
bibliography: flippant.bib
---

@@

Mean values of fit constant $\alpha$ correspond with 
`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
respectively, very well to the prior manual analysis by 
@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
of the data we conclude in @ploier_perturbed_submitted that the mutant 
rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
form, contrary to the wild type, which is reconstituting as a homodimer. 
`flippant` analysis of the data, shows identical trends and close matches of the
results, supporting identical conclusions.
